### 2013-12-15 proposal/proposal/chapter3.tex
changes

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3in]{Figures/avg_task_ws_done.eps}
\includegraphics[width=3in]{Figures/avg_qos_ws_done.eps}
\includegraphics[width=3in]{Figures/avg_avail_ws_done.eps}
\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
\end{figure}

>>>>

\begin{figure}[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=2.5in]{Figures/avg_task_ws_done.eps}
\includegraphics[width=2.5in]{Figures/avg_qos_ws_done.eps}
\includegraphics[width=2.5in]{Figures/avg_avail_ws_done.eps}
\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
\end{figure}
